# Human activity grading prediction

The dataset contains the variables measured from accelerometers on the participants and grades
assigned to the quality of their exercises. I predict the grades by the variables.

## Data loading and preprocessing

The dataset has many columns filled by NA. I remove these columns and first 7 columns containing
dates and other metainformation.

```{r}
library(caret)
pml <- read.csv("pml-training.csv", na.strings=c("NA", "", "#DIV/0!"))
pml <- pml[,colSums(is.na(pml)) < 19000]
pml <- pml[,-(1:7)]
```

## Train and test sets

I assign 60% of data to the training set and remaining 40% to the test set.

```{r}
set.seed(666)
trainIdx <- createDataPartition(y=pml$classe, p=0.6, list=F)
train <- pml[trainIdx,]
test <- pml[-trainIdx,]
```

## Machine learning

I use random forests with 25-reps bootstrap.

```{r}
set.seed(666)
fit <- train(classe~., data=train, method="rf")
fit
```

The cross-validation error is `r round(100 * (1 - max(fit$results$Accuracy)), 1)`%.

I test the random forest on the test data.

```{r}
predictions <- predict(fit, newdata=test)
confusionMatrix(predictions, test$classe)
```

The test set error is `r round(100 * (1 - mean(predictions == test$classe)), 1)`%.
